---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{coordconvert}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

You can install the development version of `{coordconvert}` like so:

```{r}
if (!require("remotes")) install.packages("remotes")
remotes::install_git("https://github.com/vtspaid/coord_converter")
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
coordconvert::run_app()

# Or if you prefer to launch in a browser
coordconvert::run_app(options = list(launch.browser = TRUE))
```

# Create Shortcut
Note: only tested on windows.

If you wish to create a shortcut to run the app use the following code to find
the path to R's executable
```{r}
paste0(R.home(), "/bin/R.exe")
```

Then paste that result with quotation marks into a .bat file on windows or a .sh 
file on Mac or Linux. Then add `-e "coordconvert::run_app(options = list(launch.browser = TRUE))" to same line.

So the final file will have a line similar to this, however the first portion
will be different depending on the result of R.home()

`"C:/PROGRA~1/R/R-45~1.1/bin/R.exe" -e "coordconvert::run_app(options = list(launch.browser = TRUE))"`

Save it to your desktop and double click it to launch the app, or optionally,
save it somewhere else and create a shortcut to it. Note that when it opens
it will also open a terminal window. The terminal window can be minimized but if 
it is closed it will close the app.

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("coordconvert")
```

```{r, error = TRUE}
covr::package_coverage()
```
